\textbf{Hardware accelerator topologies in heterogeneous systems: an evaluation in the security domain}

### 2019-12-08 reports/paper.tex
wording

The core Simon cipher functionality is implemented as the core IP and is
re-utilized to build three different accelerator types: memory-mapped
(loosely-coupled), RoCC (tightly-coupled and hybrid). In essence the the
accelerators are built by constructing wrappers around the common core.

@@

The memory-mapped accelerator can operate in two different ways: i) automatic
operation --- ECB mode only, in which all necessary rounds are performed over a word until
completion of encryption/decryption process, or ii) interactive or single operation, where
software issues one round at a time, which enables software implementation of
CBC or other modes.

@@

% TODO small interpretation paragraph here
The hybrid accelerator is significantly faster than all other implementations
tested. This is to be expected since the accelerator itself performs the memory
requests without intervention of the CPU, directly into the memory bus. The
memory-mapped accelerator in the automatic mode comes in as second fastest. This
is also to be expected in comparison with the RoCC accelerator for example,
since the latter is run in interactive mode, that is, the application code
issues each round sequentially and sequential rounds are not immediately
executed by the CPU, due to buffering and communication logic in the RoCC
adapter fabric, in contrast to the former where rounds occur immediately (next
clock cycle) one after the other.

@@

It is of note that while this work implements a cryptographic primitive that can
be used in-hardware to enable acceleration of ciphers, it is a proof-of-concept
level rudimentary implementation.

>>>>

The core Simon cipher functionality is implemented as the core IP and is
re-utilized to build three different accelerator types: memory-mapped I/O
(MMIO, loosely-coupled), RoCC (tightly-coupled and hybrid). In essence the the
accelerators are built by constructing wrappers around the common core.

@@

The MMIO accelerator can operate in two different ways: i) automatic
operation --- ECB mode only, in which all necessary rounds are performed over a word until
completion of encryption/decryption process, or ii) interactive or single operation, where
software issues one round at a time, which enables software implementation of
CBC or other modes.

@@

% TODO small interpretation paragraph here
The hybrid accelerator is significantly faster than all other implementations
tested. This is to be expected since the accelerator itself performs the memory
requests without intervention of the CPU, directly into the memory bus. The
MMIO accelerator in the automatic mode comes in as second fastest. This
is also to be expected in comparison with the RoCC accelerator for example,
since the latter is run in interactive mode, that is, the application code
issues each round sequentially and sequential rounds are not immediately
executed by the CPU, due to buffering and communication logic in the RoCC
adapter fabric, in contrast to the former where rounds occur immediately (next
clock cycle) one after the other.

@@

It is of note that while this work implements a cryptographic primitive that can
be used in-hardware to enable acceleration of ciphers, it is a proof-of-concept
level, rudimentary implementation.
